---
scene: 0
title: "Demo Slides"
subtitle: "A work in progress!"
author: "Garrick Aden-Buie & Silvia Canelón"
date: '2021-07-07'
output:
  xaringan::moon_reader:
    lib_dir: "assets/libs"
    css:
      - assets/css/js4shiny-xaringan-base.css
      - assets/css/tachyons.min.css
      - assets/css/js4shiny-xaringan-extra.css
    includes:
      after_body: assets/html/js4shiny-includes.html
    seal: false
    chakra: assets/js/remark.0.14.1.min.js
    mathjax: NULL
    nature:
      ratio: 16:9
      slideNumberFormat: "%current%"
      highlightStyle: docco
      highlightLines: true
      countIncrementalSlides: true
---

class: title

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width = 10,
  fig.height = 6,
  fig.retina = 2,
  warning = FALSE,
  message = FALSE
)
source(here::here("static", "slides", "R", "components.R"))
# use_placeholders(TRUE, TRUE)
xaringanExtra::use_xaringan_extra(c("tile_view", "panelset", "share_again"))
xaringanExtra::use_editable(id = rmarkdown::metadata$title)
```

```{r js4shiny, echo=FALSE}
js4shiny::html_setup(stylize = c("fonts", "variables", "code"))
```

`r title_slide()`

---
name: first-demo
class: fullscreen

.panelset.sideways.pl2.h-100[

```{r echo=FALSE}
# this function was added to components.R
# it creates two panels, one with a copy of the slide (found by name)
# and another panel with the markdown source for the slide (as seen by remark)
# (If the slide source is complicated, you can set source_panel = NULL and 
# manually add the source code in a panel.)
slide_source_panels("fonts")
```

]

---
class: fullscreen

.panelset.sideways.pl2.h-100[

```{r echo=FALSE}
slide_source_panels("html-resources")
```

.panel[.panel-name[Notes]

## Good?

## Bad?

## What do you think?

The slides are actually in the deck in a later section.
I put them at the end in an "Appendix".

The source is pulled from the compiled source, so you can't see R Markdown bits.

]

]

---
class: fullscreen

.panelset.sideways.pl2.h-100[

```{r echo=FALSE}
slide_source_panels("break-javascript")
```

.panel[.panel-name[Notes]

This slide doesn't look _perfect_ so somethings that rely on absolute positioning may be a little bit weird. Most basic xaringan stuff will probably look okay, though.

]

]

---
class: fullscreen

.panelset.sideways.pl2.h-100[

```{r echo=FALSE}
slide_source_panels("first-demo", source_panel = NULL)
```

.panel[.panel-name[Source]

This is where it gets **meta**.
We're looking at a slide we saw earlier in the deck!

This is the code I used to create that slide.

````markdown
---
name: first-demo
class: fullscreen

.panelset.sideways.pl2.h-100[

```{r echo=FALSE}`r ''`
slide_source_panels("fonts")
```

]
````

I had to manually make this **Source** panel because it includes an Rmd chunk.

]

]
---
class: center middle

# Appendix

---
class: break break-javascript
name: break-javascript

# JavaScript inspired break

.absolute.top-1.left-1[break break-javascript]

---
name: fonts

# Fonts

.mh-auto.w-80.f5.mt4[
.f-lato[Lato (body)] .fr.code[.f-lato]

.f-nunito[Nunito Sans] .fr.code[.f-nunito]

.f-marker[Marker] .fr.code[.f-marker]

.f-source-code[Source Code Pro] .fr.code[.f-source-code]
]

---
name: html-resources

# HTML Resources

* Mastering Shiny: Advanced UI<br>
  https://mastering-shiny.org/advanced-ui.html

* FrontEnd Masters Handbook<br>
  https://frontendmasters.com/books/front-end-handbook/2019/

* Interneting is Hard<br>
  https://internetingishard.com/

* HTML Semantics Cheat Sheet<br>
  https://learn-the-web.algonquindesign.ca/topics/html-semantics-cheat-sheet/
